%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large May Madi Aung}} & Email : \href{mailto:maymadiaung99@gmail.com}{maymadiaung99@gmail.com}\\
  \href{linkedin.com/in/maymadi}{linkedin.com/in/maymadi} & Mobile : \href{tel:+6581861415}{+65 8186 1415} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore Institute of Technology}{Singapore}
      {BEng (Hons) Information and Communications Technology (Software Eng);  GPA: 4.27}{Aug. 2020 -- Jan. 2024}
    \resumeSubheading
      {Singapore Polytechnic}{Singapore}
      {Diploma In Infocomm Security Management}{Apr. 2017 -- Apr. 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GetGo Carsharing}{Singapore}
      {Junior Developer}{Jan 2024 - Present}
      \resumeItemListStart
        \resumeItem{ASP .NET}
          {Developed the backend system for GetGo’s new architecture under a development Vehical and Operation Team.}
        \resumeItem{Data Dog}
          {Assisted the organisation in Distributed Tracing using Datadog. }
          \resumeItem{Jenkins}
          {Created CI/CD pipelines in Jenkins for GetGo 2.0.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {GetGo Carsharing}{Singapore}
      {Junior Dev (Intern)}{Jan 2023 - Dec 2023}
      \resumeItemListStart
        \resumeItem{ASP.NET}
          {Developed the backend system for a Fleet Management System using ASP.NET and employing the microservice
          architecture, resulting in a significant 50\% reduction in the time required to respond, resolve, and reactivate vehicles.}
        \resumeItem{Swift}
          {Successfully implemented enhancements in the Fleet Operator Application (iOS), leading to a notable 50\% increase in
          the number of completed maintenance jobs.}
      \resumeItemListEnd

    \resumeSubheading
      {Accenture}{Singapore}
      {Java Dev (Intern)}{Summer 2021 and 2022}
      \resumeItemListStart
        \resumeItem{System Integration Testing}
          {Conducted SIT on Client's Project and effectively reported 60\% of identified bugs to
          developers, ensuring prompt resolution and improved software quality.}
        \resumeItem{Java}
          {Utilized Java programming to implement bug fixes in the UAT (User Acceptance Testing) environment, resulting in a
          20\% decrease in the delivery timeline and enhanced project efficiency.}
        \resumeItem{SQL Database}
          {Demonstrated proficiency in data mining techniques to gather accounts for testing purposes, contributing to
          comprehensive and thorough test coverage.}
         \resumeItem{Jenkins}
          {Acquired familiarity with Jenkins Pipeline, enabling the continuous deployment of code and driving a remarkable 20\%
          improvement in customer experience through faster and more efficient software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {DBS Bank}{Sinapore}
      {Risk Analyst (Intern)}{Apr 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{SharePoint Automation}
          {Spearheaded the automation of the team's SharePoint site, specifically the TS Audit Portal, to streamline the auditing
          process, resulting in a notable 30\% reduction in audit time. This optimization allowed the team to allocate more time
          and attention to critical tasks.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Data Analytic Dashboard, NHGP}
    {Successfully develop a Data Analytic Dashboard
    using the R Shiny Framework, facilitating insightful data analysis and visualization.Implemented version control practices using Git, enabling seamless collaboration and code management within the
    development team.}
    \resumeSubItem{Hotel Concierge Web Portal}
      {Successfully guided the team in developing a robust MVC (Model-View-Controller) application using ASP.NET (C#),
      facilitating an effective learning experience in object-oriented design, software design patterns and best practices.}
    \resumeSubItem{Pentesting Tool, DSO}
      {Engineered and implemented automation solutions for Web Penetration Testing and Client-Side Penetration Testing,
      utilizing C and Java programming languages.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
 \section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Java, Python, C/C++, C#, Kotlin, Swift, R, JavaScript, HTML/CSS, SQL } \\
      \textbf{Technologies}{: AWS, Solace, Hadoop, Datadog }\\
      \textbf{Frameworks}{: ASP.NET, Node.js, Next.js, React, Flask, JUnit, Tailwind } \\
      \textbf{Developer Tools}{: Git, Docker, AWS Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse, Jenkins } 
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
